Two years of explicit CiTO annotations

### 2022-11-13 article.Rmd
Renamed the figures according to the submission system

![Screenshot of the citation statements for an article where the
*objective of project or action* qualifier is used to annotate the citation with their
CiTO intentions.](images/datamodel.png)

@@

![Screenshot of the Scholia Citation Typing Ontology page showing the
daily statistics.](images/scholiaStats.png)

@@

![Citation network consisting only of citations annotated with **[cito:usesMethodIn]**.
Articles with explicit CiTO annotation are shown in red. The Wikidata SPARQL query
used to create this diagram is available from
[https://gist.github.com/egonw/1c8bc99373a24075838ee19976c74856](https://gist.github.com/egonw/1c8bc99373a24075838ee19976c74856).](images/usesMethodInNetwork.png)

@@

![Screenshot of the "Most reused articles" section of the Scholia page for the
*Journal of Cheminformatics*. Based on CiTO annotation available in Wikidata, the ten
most reused articles are shown.](images/mostUsedInJCheminf.png)

>>>>

![Screenshot of the citation statements for an article where the
*objective of project or action* qualifier is used to annotate the citation with their
CiTO intentions.](images/figure1.png)

@@

![Screenshot of the Scholia Citation Typing Ontology page showing the
daily statistics.](images/figure2.png)

@@

![Citation network consisting only of citations annotated with **[cito:usesMethodIn]**.
Articles with explicit CiTO annotation are shown in red. The Wikidata SPARQL query
used to create this diagram is available from
[https://gist.github.com/egonw/1c8bc99373a24075838ee19976c74856](https://gist.github.com/egonw/1c8bc99373a24075838ee19976c74856).](images/figure3.png)

@@

![Screenshot of the "Most reused articles" section of the Scholia page for the
*Journal of Cheminformatics*. Based on CiTO annotation available in Wikidata, the ten
most reused articles are shown.](images/figure4.png)
